---
title: "Connectivity - EI"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    self_contained: true
    thumbnails: true
    lightbox: true
    gallery: false
    highlight: tango
    code_folding: "hide"
  html_document:
    code_folding: "hide"
    latex_engine: xelatex
---




```{r, message=FALSE, warning=FALSE, echo=FALSE}

library(readxl)
library(itsadug)
library(mgcv)
library(mgcViz)
library(tidyverse)
library(visreg)    # GAM model visualisation
library(permutes)

library(afex)       # nouveau package, surveiller les MAJ
library(lme4)
library(RVAideMemoire)
library(LMERConvenienceFunctions)
library(phia)
library(multcomp)
library(lmerTest)
library(emmeans)
library(ggpubr)
library(ggeffects)
library(DHARMa)
library(glmmTMB)
library(splines)



```

J. Jung, R. Bouet, H. Catenoix, A. Montavont, J. Isnard, S. Boulogne, M. Guénot, P. Ryvlin, S. Rheims (2022) The neural bases of ictal hypoxemia during Temporal Lobe Seizures. Humain Brain Mapping      

https://pubmed.ncbi.nlm.nih.gov/???????

Focal seizures originating from the temporal lobe are commonly associated with peri-ictal hypoxemia (PIH). During the course of temporal lobe seizures, epileptic discharges often spread within various parts of the temporal lobe but also possibly insula and frontal lobe. The link between spatial propagation of the seizure discharges and PIH is still unclear. 
Methods : The present study investigates the involvement of several brain structures including medial temporal structures, temporal pole, anterior insula and frontal cortex in the occurrence of PIH. Using quantitative indices obtained during SEEG (stereoencephalography) recordings in 38 patients, we evaluated the epileptogenicity, the spatial propagation and functional connectivity between those structures during seizures leading to PIH.   

Key words:   
GLM; Gamma distribution; Wilcoxon; LRT; parallel    



# EI

## Load datas

Here we extract datas from .txt file.   

```{r, message=FALSE, warning=FALSE}
file_path = "/Users/romain/Study/Rheins/Desaturation_Coherence/Datas_raw/EI/EI_JJ.txt"
datas <- read.table(file_path,
                    dec = ".",
                    header = TRUE)

datas %>%
  gather(key = "Structure",
         value = "EI",
         -Patname, -desat) %>%
  drop_na() %>%
  mutate(Structure = case_when(Structure == "hippoc_ant" ~ "Ant Hippo",
                               Structure == "hippoc_post" ~ "Post Hippo",
                               Structure == "amygdale" ~ "Amygdala",
                               Structure == "cing_ant" ~ "ACC",
                               Structure == "insula_ant" ~ "Ant Insula",
                               Structure == "insula_post" ~ "Post Insula",
                               Structure == "CTL" ~ "Lat Temp",
                               Structure == "frontal_lat" ~ "Lat Front",
                               Structure == "COF" ~ "OFC",
                               Structure == "pole_temp" ~ "Pole Temp")) %>%
  filter(Structure != "Lat Front" & Structure != "Post Insula" & Structure != "Post Hippo") %>% 
  mutate(Structure = factor(Structure, levels = c("Ant Hippo", "Amygdala", "Pole Temp", "Lat Temp", "Ant Insula", "OFC", "ACC"))) %>%
  mutate(Structure = as.factor(Structure)) %>%
  data.frame() -> datas



datas %>%
  dplyr::select(-Patname) %>%
  gtsummary::tbl_summary(by = "Structure") %>%
  gtsummary::add_p()

```

## Display

To explore behaviour raw datas.   

```{r, message=FALSE, warning=FALSE}

datas %>%
  ggplot(aes(x = Structure, y = EI, fill = Structure)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA) +
    coord_cartesian(ylim=c(-0.001, 0.03)) +
  scale_fill_grey() + 
  theme_classic() +
  coord_flip() +
  theme(legend.position = "none",
        axis.title.x = element_text(size = 14, face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10, angle = 0, hjust = 1),
        axis.text.y = element_text(face = "bold", size = 12, angle = 0, hjust = 1)) +
  labs(x = "",
       y = "Epileptogenicity Index")

```


## Stat

EI is value define between 0 and 1, so binomial distribution.   
Some structures have only O values. So we couldn't use glm models.    
Here we use Wilcoxon test to compare EI for all combinaison of structure.   

```{r, message=FALSE, warning=FALSE}

test.w.struct <- data.frame(Structure.A = character(),
                            Structure.B = character(),
                            p.value   = double())

all.comb.struct <- combn(unique(datas$Structure), 2, simplify = TRUE)

for (xi.struct in c(1:dim(all.comb.struct)[2])){

  test.w.tamp <- wilcox.test(filter(datas, Structure == all.comb.struct[1, xi.struct])$EI,
                             filter(datas, Structure == all.comb.struct[2, xi.struct])$EI,
                             alternative = "greater",
                             paired = FALSE,
                             exact = TRUE,
                             correct = FALSE,
                             conf.int = TRUE)

  test.w.struct %>% 
    add_row(Structure.A = all.comb.struct[1, xi.struct],
            Structure.B = all.comb.struct[2, xi.struct],
            p.value = round(test.w.tamp$p.value, 8)) -> test.w.struct
}

test.w.struct

```



# TF

## Load datas

```{r, warning=FALSE, fig.align='center' }
filename.TF <- "/Users/romain/Study/Rheins/Desaturation_Coherence/Datas_preprocessed/Mesures/extract_tf_sample_TF_sampl_corrige_doubleCrise_TF_sampl.txt"

filename.Desat <- "/Users/romain/Study/Rheins/Desaturation_Coherence/Datas_preprocessed/Mesures/Desat_parametres.txt"

datas.TF    <- read.table(filename.TF, header = TRUE)
datas.Desat <- read.table(filename.Desat, header = TRUE)


datas.TF %>%
  filter(Win != "BASELINE" & Win != "pre_ONSET" & Win!= "POST_SEIZURE") %>%
  filter(Structure != "frontallat" & Structure != "insulapost" & Structure != "hippocpost") %>%
  mutate(Win = factor(Win, levels = c("ONSET", "MID_SEIZURE", "END_SEIZURE"))) %>%
  drop_na(Mesure) %>%
  mutate(Desat = Desat,
         Mesure_pos = 0.001 + Mesure + abs(min(Mesure))) -> datas.TF


datas.Desat %>%
  dplyr::select(-desat) %>%
  right_join(datas.TF) %>%
  filter(Win != "BASELINE", Win != "pre_ONSET") %>%
  mutate(Desat_Win = case_when(is.na(onset_desat) ~"n",
                               Win == "pre_ONSET" & onset_desat <= 0 ~ "o",
                               Win == "pre_ONSET" & onset_desat > 0 ~ "n",
                               Win == "ONSET" & onset_desat.1 == "Y" ~ "o",
                               Win == "ONSET" & onset_desat.1 == "N" ~ "n",                               
                               Win == "MID_SEIZURE" & mid_desat == "Y" ~ "o",
                               Win == "MID_SEIZURE" & mid_desat == "N" ~ "n",
                               Win == "END_SEIZURE" & end_desat == "Y" ~ "o",
                               Win == "END_SEIZURE" & end_desat == "N" ~ "n",
                               Win == "POST_SEIZURE" & post_desat == "Y" ~ "o",
                               Win == "POST_SEIZURE" & post_desat == "N" ~ "n")) %>%
  mutate(Desat_Win = as.factor(Desat_Win)) %>%
  dplyr::select(-fin, -EI,
               -duree_desat, -nadir_desat, -duree_crise, -mid_sz_onset,
                -mid_desat, -onset_desat.1, -end_desat, -post_desat,
               -onset_desat, -Desat, -Mesure) -> datas.TF


rm(datas.Desat)

datas.TF %>%
    dplyr::select(-Subject) %>%
    gtsummary::tbl_strata(strata = Structure,
               .tbl_fun = ~ .x %>%
                         gtsummary::tbl_summary(by = Desat_Win, missing = "no") %>%
                         gtsummary::add_n(),
               .header = "**{strata}**"
              )

```


## Display

To explore behaviour raw datas.   

```{r, warning=FALSE, fig.align='center' }

datas.TF %>%
  ggplot(aes(x = Win, y = Mesure_pos, fill = Desat_Win)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  facet_wrap(~Structure, scales = "free_y") + 
  scale_fill_grey() + 
  theme_classic() +
  coord_cartesian(ylim=c(-0, 30)) +
  theme(legend.direction = "vertical",
        legend.box = "horizontal",
        legend.position = c(0.7,0.01),
        legend.justification = c(0, 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 12, face = "bold"),
        axis.text.x = element_text(face = "bold", size = 12, angle = 45, hjust = 1),
        axis.text.y = element_text(face = "bold", size = 10, angle = 0, hjust = 1)) +
  labs(fill = "Occurrence of PIH",
       x = "",
       y = "Ictal Activity [1-50]Hz")

```

## Stat

### Model

Here we use afex package to fit power according to 3 fixed factor and Subject factor as random.   
Power is gamma distribution with log link.   
LRT is used compute pValues.    

This is very time consuming so we use a parallel computing.    

```{r, message=FALSE, warning=FALSE}
load(file = "/Users/romain/Study/Rheins/Desaturation_Coherence/Scripts/models_TF_gamma_V07.Rdata")

# require(parallel)
# (nc <- detectCores()) # number of cores
# cl <- makeCluster(rep("localhost", nc)) # make cluster
# clusterEvalQ(cl, library(optimx)) # need to load optimx in cluster


# mixed.TF.04.g <- mixed(Mesure_pos ~ (Structure + Win + Desat_Win)^3 + ( 1| Subject),
#                        data = datas.TF,
#                        family = Gamma(link = "log"),
#                        method = "LRT",
#                        verbose = FALSE,
#                        all_fit = FALSE,
#                        expand_re = TRUE,
#                        cl = cl)



# 
#  save(mixed.TF.04.g,
#       file = "/Volumes/Backup DD/From_BAIE/Rheins/Desaturation_Coherence/Scripts/models_TF_gamma_V07.Rdata")

```

```{r, warning=FALSE, fig.align='center' }
anova(mixed.TF.04.g)
```

We find a 3 way interaction.    

### Post-Hoc

Here we interest only on **Desat_Win:Win:Structure**.     

```{r, warning=FALSE, fig.align='center' }
PH.emmeans <- emmeans(mixed.TF.04.g, c("Desat_Win", "Win"),
                      by = c("Structure"))

des_cont <- list("Onset_O_N" =       c(-1, 1, 0, 0, 0, 0),
                 "MID_SEIZURE_O_N" = c(0, 0, -1, 1, 0, 0),
                 "END_SEIZURE_O_N" = c(0, 0, 0, 0, -1, 1))

test(contrast(regrid(PH.emmeans), des_cont, adjust = "FDR"), side = ">")

```

To explore behaviour estimate effects.   

```{r, warning=FALSE, fig.align='center' }

emmip(mixed.TF.04.g, 
      Desat_Win ~ Win|Structure,
      cov.reduce = FALSE,
      type = "response")-> p


pd <- position_dodge(0.3)

p$data %>%
  ggplot(aes(x = xvar, y = yvar, color = Desat_Win)) +
  facet_wrap(~Structure, scales = "free_y") + 
  geom_errorbar(aes(ymin = yvar-SE, ymax = yvar+SE), 
                  width = .1, position = pd) +
  geom_point(position = pd, size = 2) +
  scale_colour_grey(start = 0.35,
                    end = 0.65) + 
  theme_classic() +
  theme(legend.direction = "vertical",
        legend.box = "horizontal",
        legend.position = c(0.7,0.01),
        legend.justification = c(0, 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 12, face = "bold"),
        axis.text.x = element_text(face = "bold", size = 12, angle = 45, hjust = 1),
        axis.text.y = element_text(face = "bold", size = 10, angle = 0, hjust = 1)) +
  labs(fill = "Occurrence of PIH",
       x = "",
       y = "Ictal Activity [1-50]Hz") 

```


# Connectivity

## Load datas

```{r, warning=FALSE, fig.align='center' }
filename.Desat <- "/Users/romain/Study/Rheins/Desaturation_Coherence/Datas_preprocessed/Mesures/Desat_parametres.txt"
datas.Desat <- read.table(filename.Desat, header = TRUE)

filename.Connect <- "/Users/romain/Study/Rheins/Desaturation_Coherence/Datas_preprocessed/Mesures/extract_tf_sample_TF_sampl_corrige_doubleCrise_Connect.txt"
datas.Connect <- read.table(filename.Connect, header = TRUE)

datas.Connect %>%
  filter(Win != "BASELINE" & Win != "pre-ONSET" & Win != "ONSET" & Win != "POST_SEIZURE") %>%
  mutate(Win = factor(Win, levels = c("MID_SEIZURE", "END_SEIZURE"))) %>%
  unique()  %>%
  mutate(Structure = case_when(Structure == "COF-amygdale" | 
                                 Structure == "cingant-amygdale" | 
                                 Structure == "frontallat-amygdale" ~ "Frontal - Amygdale",
                               Structure == "COF-hippocant" |  
                                 Structure == "cingant-hippocant" |
                                 Structure == "frontallat-hippocant" ~ "Frontal - Hippo",
                               Structure == "COF-CTL" | 
                                 Structure == "cingant-CTL" |
                                 Structure == "frontallat-CTL" ~ "Frontal - Temp_Lat",
                               Structure == "COF-insulaant" | 
                                 Structure == "cingant-insulaant" |
                                 Structure == "frontallat-insulaant" ~ "Frontal - Insula",
                               Structure == "COF-poletemp" |
                                 Structure == "cingant-poletemp" |
                                 Structure == "frontallat-poletemp" ~ "Frontal - Pole",
                               Structure == "amygdale-CTL" ~ "Amygdale - Temp_Lat",
                               Structure == "hippocant-CTL" ~ "Hippo - Temp_Lat",
                               Structure == "insulaant-CTL" ~ "Insula - Temp_Lat",
                               Structure == "amygdale-insulaant" ~ "Amygdale - Insula",
                               Structure == "amygdale-hippocant" ~ "Amygdale - Hippo",
                               Structure == "hippocant-insulaant" ~ "Hippo - Insula",
                               Structure == "amygdale-poletemp" ~ "Amygdale - Pole",
                               Structure == "hippocant-poletemp" ~ "Hippo - Pole",
                               Structure == "CTL-poletemp" ~ "Temp_Lat - Pole",
                               Structure == "insulaant-poletemp" ~ "Insula - Pole"))  %>%
  mutate(Structure = as.factor(Structure)) %>%
  filter(Structure == "Frontal - Amygdale" | 
         Structure == "Frontal - Hippo" | 
         Structure == "Frontal - Temp_Lat" | 
         Structure == "Frontal - Insula" |
         Structure == "Frontal - Pole" |
         Structure == "Amygdale - Temp_Lat" | 
         Structure == "Hippo - Temp_Lat" | 
         Structure == "Insula - Temp_Lat" | 
         Structure == "Amygdale - Insula" | 
         Structure == "Amygdale - Hippo" | 
         Structure == "Hippo - Insula" |
         Structure == "Amygdale - Pole" |
         Structure == "Hippo - Pole" |
         Structure == "Temp_Lat - Pole" |
         Structure == "Insula - Pole") %>%
  na.omit(Mesure) -> datas.Connect.Clust



datas.Desat %>%
  dplyr::select(-desat) %>%
  right_join(datas.Connect.Clust) %>%
  mutate(Desat_Win = case_when(is.na(onset_desat) ~"n",
                               Win == "MID_SEIZURE" & mid_desat == "Y" ~ "o",
                               Win == "MID_SEIZURE" & mid_desat == "N" ~ "n",
                               Win == "END_SEIZURE" & end_desat == "Y" ~ "o",
                               Win == "END_SEIZURE" & end_desat == "N" ~ "n")) %>%
  mutate(Desat_Win = as.factor(Desat_Win)) %>%
  filter(Bd_Freq == "broadband") %>%
  dplyr::select(-duree_desat, -nadir_desat, -duree_crise, -mid_sz_onset,
                -mid_desat, -onset_desat.1, -end_desat, -post_desat,
                -onset_desat, -Desat, -Bd_Freq)  -> datas.Conn

rm(datas.Connect.Clust, datas.Desat)

datas.Conn %>%
    dplyr::select(-Subject) %>%
    gtsummary::tbl_strata(strata = Structure,
               .tbl_fun = ~ .x %>%
                         gtsummary::tbl_summary(by = Desat_Win, missing = "no") %>%
                         gtsummary::add_n(),
               .header = "**{strata}**"
              )

```

## Display

To explore behaviour raw datas.   

```{r, warning=FALSE, fig.align='center' }
datas.Conn %>%
  ggplot(aes(x = Win, y = Mesure, fill = Desat_Win)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  facet_wrap(~Structure, scales = "free_y") +
  scale_fill_grey() + 
  theme_classic() +
  theme(legend.direction = "vertical",
        legend.box = "horizontal",
        legend.position = c(0.77,0.01),
        legend.justification = c(0, 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14, face = "bold"),
        axis.text.x = element_text(face = "bold", size = 10, angle = 45, hjust = 0.5, vjust = 0.65),
        axis.text.y = element_text(face = "bold", size = 10, angle = 0, hjust = 1)) +
  labs(fill = "Occurrence of PIH",
       x = "",
       y = "Functional Connectivity")

datas.Conn %>%
  ggplot(aes(x = Win, y = Mesure, fill = Desat_Win)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  scale_fill_grey() + 
  theme_classic() +
  coord_cartesian(ylim=c(0, 0.15)) +
  theme(legend.direction = "vertical",
        legend.box = "horizontal",
        legend.position = c(0.3,1),
        legend.justification = c(0, 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14, face = "bold"),
        axis.text.x = element_text(face = "bold", size = 12, angle = 0, hjust = 0.5, vjust = 0.5),
        axis.text.y = element_text(face = "bold", size = 10, angle = 0, hjust = 1)) +
  labs(fill = "Occurrence of PIH",
       x = "",
       y = "Functional Connectivity") 

datas.Conn %>%
  ggplot(aes(x = Structure, y = Mesure, fill = Structure)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  scale_fill_grey() + 
  theme_classic() +
  coord_cartesian(ylim=c(0, 0.13)) +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 14, face = "bold"),
        axis.text.x = element_text(face = "bold", size = 12, angle = 60, hjust = 0.6, vjust = 0.65),
        axis.text.y = element_text(face = "bold", size = 10, angle = 0, hjust = 1)) +
  labs(fill = "Occurrence of PIH",
       x = "",
       y = "Functional Connectivity") 
```

## Stat

### Model

Here we use afex package to fit connectivity according to 3 fixed factors and 2 random factors.   
Power is gamma distribution with log link.   
LRT is used compute pValues.    

This is very time consuming so we use a parallel computing.    

```{r, warning=FALSE, fig.align='center' }

load(file = "/Users/romain/Study/Rheins/Desaturation_Coherence/Scripts/Model_Conn_V03_Broad.RData")

#
# require(parallel)
# (nc <- detectCores()) # number of cores
# cl <- makeCluster(rep("localhost", nc)) # make cluster
# clusterEvalQ(cl, library(optimx)) # need to load optimx in cluster

# mixed.Con.03 <- mixed(Mesure+0.0001 ~ (Desat_Win + Structure + Win)^3 + (1|Subject) + (1|Structure), 
#                       family = Gamma(link = "log"),
#                       data = datas.Broad,
#                       method = "LRT",
#                       verbose = FALSE)
#plot(simulateResiduals(fittedModel = mixed.Con.03$full_model, n = 1000))

anova(mixed.Con.03)
```

### Post-Hoc

```{r, warning=FALSE, fig.align='center' }
PH.emmeans <- emmeans(mixed.Con.03, c("Desat_Win"), by = "Win")

des_cont <- list("O-N" = c(-1, 1))
test(contrast(regrid(PH.emmeans), des_cont, adjust = "FDR"), side = "both")

emmip(mixed.Con.03, 
      Desat_Win ~ Win,
      cov.reduce = FALSE,
      type = "response") -> p.01

p.01$data %>%
  ggplot(aes(x = Win, y = yvar, color = Desat_Win)) +
  geom_errorbar(aes(ymin = yvar-SE, ymax = yvar+SE), 
                  width = .1, position = pd) +
  geom_point(position = pd, size = 2) +
  scale_colour_grey(start = 0.35,
                    end = 0.65) + 
  theme_classic() +
  theme(legend.direction = "vertical",
        legend.box = "horizontal",
        legend.position = c(0.45,1),
        legend.justification = c(0, 1),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 12, face = "bold"),
        axis.text.x = element_text(face = "bold", size = 12, angle = 45, hjust = 1),
        axis.text.y = element_text(face = "bold", size = 10, angle = 0, hjust = 1)) +
  labs(fill = "Occurrence of PIH",
       x = "",
       y = "Functional Connectivity") 


PH.emmeans <- emmeans(mixed.Con.03, c("Structure"), type = "response")

test(contrast(pairs(PH.emmeans), adjust = "FDR"), side = "both")[,c(1:3, 7)] %>%
  filter(p.value < 0.05) %>%
  mutate(ratio = round(ratio, 3),
         SE       = round(SE, 3),
         p.value  = round(p.value, 6))


emmip(mixed.Con.03, 
      ~ Structure,
      cov.reduce = FALSE,
      type = "response") -> p.00

p.00$data %>%
  ggplot(aes(x = Structure, y = yvar, color = Structure)) +
  geom_errorbar(aes(ymin = yvar-SE, ymax = yvar+SE), 
                  width = .1, position = pd) +
  geom_point(position = pd, size = 2) +
  scale_colour_grey(start = 0.35,
                    end = 0.65) + 
  theme_classic() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 12, face = "bold"),
        axis.text.x = element_text(face = "bold", size = 12, angle = 45, hjust = 1),
        axis.text.y = element_text(face = "bold", size = 10, angle = 0, hjust = 1)) +
  labs(fill = "Structure",
       x = "",
       y = "Functional Connectivity") 
```

# Nadir

## Load datas

```{r, warning=FALSE, fig.align='center' }
filename.TF <- "/Users/romain/Study/Rheins/Desaturation_Coherence/Datas_preprocessed/Mesures/extract_tf_sample_TF_sampl_corrige_doubleCrise_TF_sampl.txt"

filename.Desat <- "/Users/romain/Study/Rheins/Desaturation_Coherence/Datas_preprocessed/Mesures/Desat_parametres.txt"

datas.TF    <- read.table(filename.TF, header = TRUE)
datas.Desat <- read.table(filename.Desat, header = TRUE)


datas.TF %>%
  filter(Desat == "o") %>%
  filter(Win != "BASELINE" & Win != "pre_ONSET" & Win!= "POST_SEIZURE") %>%
  filter(Structure != "frontallat" & Structure != "insulapost" & Structure != "hippocpost") %>%
  mutate(Win = factor(Win, levels = c("ONSET", "MID_SEIZURE", "END_SEIZURE"))) %>%
  drop_na(Mesure) %>%
  mutate(Desat = Desat,
         Mesure_log = log(0.001 + Mesure + abs(min(Mesure))),
         Mesure_pos = 0.001 + Mesure + abs(min(Mesure))) -> datas.TF


datas.Desat %>%
  dplyr::select(-desat) %>%
  right_join(datas.TF) %>%
  filter(Win != "BASELINE", Win != "pre_ONSET") %>%
  mutate(Desat_Win = case_when(is.na(onset_desat) ~"n",
                               Win == "pre_ONSET" & onset_desat <= 0 ~ "o",
                               Win == "pre_ONSET" & onset_desat > 0 ~ "n",
                               Win == "ONSET" & onset_desat.1 == "Y" ~ "o",
                               Win == "ONSET" & onset_desat.1 == "N" ~ "n",                               
                               Win == "MID_SEIZURE" & mid_desat == "Y" ~ "o",
                               Win == "MID_SEIZURE" & mid_desat == "N" ~ "n",
                               Win == "END_SEIZURE" & end_desat == "Y" ~ "o",
                               Win == "END_SEIZURE" & end_desat == "N" ~ "n",
                               Win == "POST_SEIZURE" & post_desat == "Y" ~ "o",
                               Win == "POST_SEIZURE" & post_desat == "N" ~ "n"),
         nadir_desat = 100-nadir_desat) %>%
  mutate(Desat_Win = as.factor(Desat_Win)) %>%
  dplyr::select(-fin, -EI,
                -duree_crise, -mid_sz_onset,
                -mid_desat, -onset_desat.1, -end_desat, -post_desat) %>%
  droplevels()-> datas.TF




datas.TF %>%
  mutate(Structure = case_when(Structure == "hippocant" ~ "Ant Hippo",
                               Structure == "amygdale" ~ "Amygdala",
                               Structure == "cingant" ~ "ACC",
                               Structure == "insulaant" ~ "Ant Insula",
                               Structure == "CTL" ~ "Lat Temp",
                               Structure == "COF" ~ "OFC",
                               Structure == "poletemp" ~ "Pole Temp"),
         Win = case_when(Win == "ONSET" ~ "Onset",
                         Win == "MID_SEIZURE" ~ "Propagation",
                         Win == "END_SEIZURE" ~ "End")) %>%
   mutate(Structure = factor(Structure, levels = c("Ant Hippo", "Amygdala", "Pole Temp", "Lat Temp", "Ant Insula", "OFC", "ACC")),
           Win = factor(Win, levels = c("Onset", "Propagation", "End"))) %>%
  mutate(Structure = as.factor(Structure)) %>%
  data.frame() -> datas.TF


rm(datas.Desat)


datas.TF %>%
  dplyr::select(-Subject, -onset_desat, -duree_desat, -Desat, -Mesure, -Mesure_log, -Desat_Win) %>%
  gtsummary::tbl_summary(by = "Structure") %>%
  gtsummary::add_p()

```


## Stat

### Model

```{r, message=FALSE, warning=FALSE, echo=FALSE}
load(file = "/Users/romain/Study/Rheins/Desaturation_Coherence/Scripts/models_TF_V08.Rdata")

# require(parallel)
# (nc <- detectCores()) # number of cores
# cl <- makeCluster(rep("localhost", nc)) # make cluster
# clusterEvalQ(cl, library(optimx)) # need to load optimx in cluster


# mixed.TF.04.g <- mixed(Mesure_pos ~ (Structure + Win + nadir_desat)^3 + ( 1| Subject),
#                        data = datas.TF,
#                        family = Gamma(link = "log"),
#                        method = "LRT",
#                        verbose = FALSE,
#                        all_fit = FALSE,
#                        expand_re = TRUE,
#                        cl = cl)


anova(mixed.TF.04.g)
```

### Post-Hoc

```{r, warning=FALSE, fig.align='center' }
load(file = "/Users/romain/Study/Rheins/Desaturation_Coherence/Article/models_nadir.Rdata")

# mixed.TF.09.g <- glmer(Mesure_pos ~ (Structure + Win + ns(nadir_desat,2))^3 +
#                                      ( 1| Subject),
#                         data = datas.TF,
#                         family = Gamma(link = "identity"))

emmip(mixed.TF.09.g, 
      Win ~ nadir_desat|Structure,
      cov.reduce = FALSE) +
      scale_colour_grey() + 
      theme_classic() +
  coord_cartesian(ylim =c(0, 150)) -> p

datas.TF %>%
  mutate(Desat =Desat) %>%
  ggplot(aes(x = nadir_desat, y = Mesure, color = Win, shape = Win)) +
    facet_wrap(~Structure) + 
    geom_line(aes(x = xvar, y = yvar), data = p$data, size = 1.4) +
    coord_cartesian(ylim =c(0, 170)) +
    scale_colour_grey() + 
    theme_classic() +
    theme(legend.direction = "vertical",
          legend.box = "horizontal",
          legend.position = c(0.7,0.25),
          legend.justification = c(0, 1),
          axis.title.x = element_text(size = 12, face = "bold", hjust = 0.14),
          axis.title.y = element_text(size = 12, face = "bold"),
          axis.text.x = element_text(face = "bold", size = 10),
          axis.text.y = element_text(face = "bold", size = 10)) +
  labs(x = "Nadir",
       y = "Ictal Activity [1-50]Hz",
       shape = "Seizure Period",
       color = "Seizure Period")

```